---
title: "Software Tools, R - Homework3 - Answer"
output: html_notebook
---

**Due date** : 29 Now 2019, 18:00

***

#### <span style="color:green">**Objectives**</span>

- Function
- Condition Statments
- Loops

***

#### <span style="color:brown">**Questions**</span>


***

**1** - A dependent function chain is defined as $h(x)=\frac{log(x)-1}{\sqrt{x}}$, $g(x)=e^{\sqrt{h(x)}}$ and $f(x)=sing(x)^{cosg(x)}$.  Create a function and solve $f(x)$ for each **x <- 4:250**. Print and **plot$f(x)$**.

```{r}
my_fun <- function() { 
  x <- 4:250
  hx <- (log(x)-1)/sqrt(x)
  gx <- exp(sqrt(hx))
  fx <- sin(gx)^(cos(gx))
  print(fx)
  plot(fx)
}
```

***

**2** - Create a function. Inside; 

  - Create **n** sizes random **x** vector which starts with minimum (**min**) and ends maximum (**max**) values
  - Define a **threshold**. *(for example: my_threshold <- 500)*
  - Find how many values in **x** vector are greater than the threshold. (you can assign as **big_numbers**)
  - If there are no any **big_numbers**, print a sentence like 'There is no big number' 
  - Else print the size (or lenght) of **big_numbers**

```{r}
my_num <- function(n, min, max, threshold) { 
  
  x <- runif(n,min,max)
  
  print(x)
  print(x > threshold)
  big_numbers <- sum(x > threshold)
  
  if (big_numbers == 0) {
    print("There is no big number")
  }else {
    print(c("The size of sample:", big_numbers))
  }
  
}
```

***

**3** - Create a function that calculates the sum of each digit of any number *(For instance, sum of digits of 385102 is 3 + 8 + 5 + 1 + 2 = 19)*. While sum is lower than 50, then add 10 to sum in a loop. In every loop, print a warning sentence.

```{r}
sumofdig <- function(x) { 
sum <- sum(as.integer(strsplit(as.character(x), "")[[1]]))
while (sum < 50) {
  print("sum is lower than 50, so I am going to add more 10")
  sum <- sum + 10
  message("new sum is : ",sum)
  }
}
```


***

***For questions, please use Ninova***

***

*I inspired from Ismail SEZEN*

***
