---
title: "Software Tools, R - Homework3 - Answer"
output: html_notebook
---

**Due date** : 29 Now 2019, 18:00

***

#### <span style="color:green">**Objectives**</span>

- Function
- Condition Statments
- Loops

***

#### <span style="color:brown">**Questions**</span>


***

**1** - A dependent function chain is defined as $h(x)=\frac{log(x)-1}{\sqrt{x}}$, $g(x)={e^\sqrt{h(x)}}$ and $f(x)=sing(x)^{cosg(x)}$.  Create a function and solve $f(x)$ for each x <- 4:250. Print and plot $f(x)$.

```{r}
chain <- function() { 
x <- 4:250
hx <- (log(x)-1)/sqrt(x)
gx <- exp(sqrt(hx))
fx <- sin(gx)^(cos(gx))
print(fx)
plot(fx)
}
```

***

**2** - Create a function that calculates number of exceedence of a specified threshold in an random x vector. If the number of exceedence is higher than threshold than print a sentence, else print another sentence for warning.

```{r}
exeedence <- function(n, min, max, threshold) { 
  x <- runif(n,min,max)
  print(x)
  print(x > 500)
  number <- sum(x > 500)
  if (number > 20) {
    print("More than 20 samples are higher than 500")
  }else {
    print("20 samples are lower than 500")
  }
}
```

***

**3** - Create a function calculates the sum of digits of any integer. For instance, sum of digits of 385102 is 3 + 8 + 5 + 1 + 2 = 19. While sum is lower than 50, then add 10 to sum and print a warning sentence.

```{r}
sumofdig <- function(x) { 
sum <- sum(as.integer(strsplit(as.character(x), "")[[1]]))
while (sum < 50) {
  print("sum is lower than 50, so I am going to add more 10")
  sum <- sum + 10
  message("new sum is : ",sum)
  }
}
```


***

***For questions, please use Ninova***

***

*I inspired from Ismail SEZEN*

***
