---
title: "Software Tools, R - Homework3"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

**Due date** : 25 Dec 2020, 23:59

***

#### <span style="color:green">**Objectives**</span>

- Function
- Condition Statments
- Loops

***

#### <span style="color:brown">**Questions**</span>

***

**1** - A dependent function chain is defined as $h(x)=\frac{log(x)-1}{\sqrt{x}}$, $g(x)=e^{\sqrt{h(x)}}$ and $f(x)=sing(x)^{cosg(x)}$.  Create a function and solve $f(x)$ for each **x <- 4:250**. Print and **plot$f(x)$**.

```{r}
my_fun <- function() { 
  
x <- 4:250

# Fill here

plot(fx)

}
```

***

**2** - Create a function. Inside; 

  - Create **n** sizes random **x** vector which starts with minimum (**min**) and ends maximum (**max**) values
  - Define a **threshold**. *(for example: my_threshold <- 500)*
  - Find how many values in **x** vector are greater than the threshold. (you can assign as **big_numbers**)
  - If there are no any **big_numbers**, print a sentence like 'There is no big number' 
  - Else print the size (or lenght) of **big_numbers**

```{r}
my_num <- function(n, min, max, threshold) { 
  
# x <- runif(n,min,max)     # You can use runif() function or different function

# big_numbers <-   (you can use this to fidn which values are bigger than threshold: (x > threshold) )

# if

# else

}
```

***

**3** - Create a function that calculates the sum of each digit of any number *(For instance, sum of digits of 385102 is 3 + 8 + 5 + 1 + 2 = 19)*. While sum is lower than 50, then add 10 to sum in a loop. In every loop, print a warning sentence.

```{r}
sumofdig <- function(x) { 
  
# You can use strsplit() function
# sum <-

# while ( ) {
#
# print("sum is lower than 50, so I am going to add more 10")
#    
#   }

}
```

***

***For questions or problems, please use Ninova***

***

*I inspired from Ismail SEZEN*

***