---
title: "New Accounts"
output: 
  revealjs::revealjs_presentation:
    theme: league
---

```{r, echo=FALSE}
knitr::opts_chunk$set(error = FALSE)
```

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(png)
library(grid)
```

## **NEW ACCOUNTS**

- Github, Researchgate, DOI Code, ORCID, Overleaf(LaTeX)
- Mendeley, Panoply, Sublime Text, Filezilla
- ArcGIS, QGIS
- Anaconda, Jupyter, Cygwin, R Studio, NCL
- Meted, Coursera, Udemy, Datacamp, Edx, Khanacademy
- Stackoverflow, Wolfram-alpha, Dropbox, Wetransfer




## Github
```{r fig.width=9, fig.height=5, echo=FALSE}
img3 <- readPNG("github.png")
 grid.raster(img3)
```
[LINK](https://github.com)

## Researchgate
```{r fig.width=9, fig.height=5, echo=FALSE}
img4 <- readPNG("researchgate.png")
 grid.raster(img4)
```
[LINK](https://www.researchgate.net)

## DOI Code - (digital object identifier) - Zenodo
```{r fig.width=9, fig.height=5, echo=FALSE}
img5 <- readPNG("zenodo-doi.png")
 grid.raster(img5)
```
[LINK](https://zenodo.org/)

## ORCID
```{r fig.width=9, fig.height=5, echo=FALSE}
img6 <- readPNG("orcid.png")
 grid.raster(img6)
```
[LINK](https://orcid.org/)

## Overleaf (LaTeX)
```{r fig.width=9, fig.height=5, echo=FALSE}
img7 <- readPNG("overleaf.png")
 grid.raster(img7)
```
[LINK](https://www.overleaf.com/)

## Mendeley
```{r fig.width=9, fig.height=5, echo=FALSE}
img8 <- readPNG("mendeley.png")
 grid.raster(img8)
```
[LINK](https://www.mendeley.com)

## Panoply
```{r fig.width=9, fig.height=5, echo=FALSE}
img9 <- readPNG("panoply.png")
 grid.raster(img9)
```
[LINK](https://www.giss.nasa.gov/tools/panoply/)

## Sublime Text
```{r fig.width=9, fig.height=5, echo=FALSE}
img10 <- readPNG("sublimetext.png")
 grid.raster(img10)
```
[LINK](https://www.sublimetext.com/)

## Filezilla
```{r fig.width=9, fig.height=5, echo=FALSE}
img11 <- readPNG("filezilla.png")
 grid.raster(img11)
```
[LINK](https://filezilla-project.org/)

## ArcGIS
```{r fig.width=9, fig.height=5, echo=FALSE}
img12 <- readPNG("arcgis.png")
 grid.raster(img12)
```
[LINK](https://www.arcgis.com/index.html)
 
## QGIS
```{r fig.width=9, fig.height=5, echo=FALSE}
img13 <- readPNG("qgis.png")
 grid.raster(img13)
```
[LINK](https://qgis.org/en/site/)

## Anaconda
```{r fig.width=9, fig.height=5, echo=FALSE}
img14 <- readPNG("anaconda.png")
 grid.raster(img14)
```
[LINK](https://www.anaconda.com)

## Jupyter
```{r fig.width=9, fig.height=5, echo=FALSE}
img15 <- readPNG("jupyter.png")
 grid.raster(img15)
```
[LINK](https://jupyter.org/install)

## Cygwin
```{r fig.width=9, fig.height=5, echo=FALSE}
img16 <- readPNG("cygwin.png")
 grid.raster(img16)
```
[LINK](https://www.cygwin.com/)

## R Studio
```{r fig.width=9, fig.height=5, echo=FALSE}
img17 <- readPNG("rstudio.png")
 grid.raster(img17)
```
[LINK](https://www.rstudio.com/)

## NCL
```{r fig.width=9, fig.height=5, echo=FALSE}
img18 <- readPNG("ncl.png")
 grid.raster(img18)
```
[LINK](https://www.ncl.ucar.edu/)

## Meted
```{r fig.width=9, fig.height=5, echo=FALSE}
img19 <- readPNG("meted.png")
 grid.raster(img19)
```
[LINK](https://www.meted.ucar.edu/)
 
## Coursera
```{r fig.width=9, fig.height=5, echo=FALSE}
img20 <- readPNG("coursera.png")
 grid.raster(img20)
```
[LINK](https://www.coursera.org)

## Udemy
```{r fig.width=9, fig.height=5, echo=FALSE}
img21 <- readPNG("udemy.png")
 grid.raster(img21)
```
[LINK](https://www.udemy.com/)

## Datacamp
```{r fig.width=9, fig.height=5, echo=FALSE}
img22 <- readPNG("datacamp.png")
 grid.raster(img22)
```
[LINK](https://www.datacamp.com/home)

## Edx
```{r fig.width=9, fig.height=5, echo=FALSE}
img23 <- readPNG("edx.png")
 grid.raster(img23)
```
[LINK](https://www.edx.org)

## Khan academy
```{r fig.width=9, fig.height=5, echo=FALSE}
img24 <- readPNG("khanacademy.png")
 grid.raster(img24)
```
[LINK](https://www.khanacademy.org/)

## Stack overflow
```{r fig.width=9, fig.height=5, echo=FALSE}
img25 <- readPNG("stackoverflow.png")
 grid.raster(img25)
```
[LINK](https://stackoverflow.com/)

## Wolfram alpha
```{r fig.width=9, fig.height=5, echo=FALSE}
img26 <- readPNG("wolfram-alpha.png")
 grid.raster(img26)
```
[LINK](https://www.wolframalpha.com/)

## Dropbox
```{r fig.width=9, fig.height=5, echo=FALSE}
img27 <- readPNG("dropbox.png")
 grid.raster(img27)
```
[LINK](https://www.dropbox.com/)

## Wetransfer
```{r fig.width=9, fig.height=5, echo=FALSE}
img28 <- readPNG("wetransfer.png")
 grid.raster(img28)
```
[LINK](https://wetransfer.com/)

